Appendix A: Multispecies models

### 2022-02-23 notebook/appendix-A.Rmd
:pen:

---
output: github_document
---

@@

- Model 1: A reasonable approximation model that does not produce very accurate forecasts, but nevertheless leads to good management decisions.
- Model 2: A reasonable approximation model that produces more accurate forecasts but leads to substantially worse management outcomes
- Model 3: The "True" Model: five-species model; functional forms and parameter values are never disclosed to the 'manager' but are used to simulate all data and management scenarios.

@@

```{r}
df <- model_5sp(0, .0, sigma = 0.01)

df %>%
    pivot_longer(tidyselect::starts_with("x"),
                    names_to = "species",
                    values_to = "biomass") %>%
    ggplot(aes(time, biomass, group= interaction(species,r), col=species)) + geom_path() + ggtitle("Unfished")
```

Starting from the unfished equilibrium,

```{r}
df <- model_5sp(0, .58, sigma = 0.01)

df %>%
    pivot_longer(tidyselect::starts_with("x"),
                    names_to = "species",
                    values_to = "biomass") %>%
    ggplot(aes(time, biomass, group= interaction(species,r), col=species)) + 
  geom_path() + ggtitle("Optimally managed")
```

@@

```{r}
## Three-species 'view' of the underlying dynamics, without fishing, starting all species from a low level

#true_observations <- model_5sp(0, 0., sigma = 0.05, x1o =.033, x2o = .033, x3o = .033, x4o = .1, x5o = .1, Tmax = 50)
true_observations <- model_5sp(0, 0, sigma = 0.05)

obs <- true_observations %>% 
  transmute(time = time, cormorant = x5, bass = x4, herring = x1+x2+x3, r=r) %>%
    pivot_longer(any_of(c("cormorant", "bass", "herring")),
                    names_to = "species",
                    values_to = "biomass")

obs %>%
    ggplot(aes(time, biomass, col = species, group = interaction(species,r))) +
    geom_path(alpha=0.4)
```

>>>>

---
output: pdf_document
title: Appendix A: Multispecies models
---

@@

We consider a simulated system described by the 5-dimensional model of a herring fishery presented in @Brias2021:

\begin{align}
\end{align}

We will assume this is the "true" model, which is unknown to managers.

While richer numerical models can successfully capture the full complexity of this five-dimensional model, we must remember that reality is always more complex than our models.
As the term implies, models intentional simplifications of reality.

- Model A: A reasonable approximation model that produces more accurate forecasts but leads to substantially worse management outcomes
- Model B: A reasonable approximation model that does not produce very accurate forecasts, but nevertheless leads to good management decisions.
- Model C: The "True" Model: five-species model; functional forms and parameter values are never disclosed to the 'manager' but are used to simulate all data and management scenarios.

@@

@@
